---
title: "Requirements"
author: "Leonie Roos"
date: "25/08/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data 


## R
Download or please update R to the latest version (or at least R version 3.4.0) from [here](https://www.r-project.org/).

## RStudio 

Download and install RStudio from the following link (if you already have RStudio, update to latest version): [RStudio weblink](https://www.rstudio.com/products/RStudio/#Desktop).

## R Packages
If asked to update packages (Update all/some/none [a/s/n]) - update all packages (answer a).

### Bioconductor

- Bioconductor

```{r eval = FALSE}
source("https://bioconductor.org/biocLite.R")
biocLite()
```

- CAGEr

```{r eval = FALSE}
biocLite("CAGEr")
```

- BSgenome Hsapiences UCSC hg38

```{r eval = FALSE}
biocLite("BSgenome.Hsapiens.UCSC.hg38")
```

- heatmaps

```{r eval = FALSE}
biocLite("heatmaps")
```

- GenomicRanges, IRanges, Biostrings
```{r eval = FALSE}
biocLite("GenomicRanges")
biocLite("IRanges")
biocLite("Biostrings")
```


### CRAN